---
title: "final_report - AM "
output: 
  pdf_document: 
    fig_width: 4
    fig_height: 3
---

```{r load-packages, message = FALSE,include = FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(htmltools)
library(dplyr)
library(ggplot2)
library(tibble)
library(cowplot)
library(class)
library(rpart)
library(car)
```

```{r,include=FALSE}
data_self <-read.csv("MTurkself.csv", header=TRUE, stringsAsFactors=FALSE)
data_provider <-read.csv("MTurkProvider.csv", header=TRUE, stringsAsFactors=FALSE)
names(data_provider)[1]<-"Session"
```

## 1.Introduction

## 2.Data overview


```{r,echo=FALSE,include=TRUE}
self_session1 <- data_self %>% filter(Session == "1")##select first week
self_session1<-subset(self_session1, select=mood1_1_angry:mood1_10_energetic)##select emotion columns
self_session1<-sapply(self_session1,FUN=mean)

provider_session1 <- data_provider %>% filter(Session == "1")##select first week
provider_session1<-subset(provider_session1, select=mood1_1_angry:mood1_10_energetic)##select emotion columns
provider_session1<-sapply(provider_session1,FUN=mean)

df_all <- cbind(self_session1,provider_session1)
df_all <- data.frame(df_all)
df_all <- rownames_to_column(df_all,var="emotions")
df_all <-pivot_longer(df_all,cols = ends_with("session1"))
df_all$emotions <- factor(df_all$emotions,levels = c("mood1_2_happy", "mood1_5_cheerful","mood1_10_energetic","mood1_6_calm", "mood1_8_relaxed","mood1_9_lonely","mood1_3_anxious","mood1_4_distressed","mood1_1_angry","mood1_7_sad"))

ggplot(df_all, aes( y= value , fill = name,x=emotions)) + 
    geom_bar(position="dodge", stat="identity",alpha = 0.8,width = 0.7)+ labs(title = "Initial subjects' rating",subtitle = "represented as the mean of every group",
    x = 'Emotions',y='value') +
scale_fill_manual(labels = c("Self", "Provider"),values = c("self_session1" = "lightskyblue","provider_session1" = "hotpink"))+  theme(axis.text.x = element_text(angle = 60 ,hjust=1))+ scale_x_discrete(labels=c("mood1_2_happy" = "Happy", "mood1_5_cheerful" = "Cheerful","mood1_10_energetic" = "Energetic","mood1_6_calm" = "Calm","mood1_8_rel2axed" = "Relaxed","mood1_9_lonely" = "Lonely","mood1_3_anxious" = "Anxious","mood1_4_distressed" = "Distressed","mood1_1_angry" = "Angry","mood1_7_sad" = "Sad"))+ guides(fill=guide_legend(title="Group"))

```

## 3.Methods and results


**Self group regression model : **
we created a multiple regression model according to the positive emotions of the participants in the self group : 
```{r,echo=FALSE,include=FALSE}
positive_self_before <- data_self %>% filter(Session == "1" | Session == "2") %>%distinct(id,.keep_all = TRUE)
positive_self_before <- subset(positive_self_before, select= c("id","mood1_2_happy","mood1_5_cheerful","mood1_6_calm","mood1_8_relaxed","mood1_10_energetic"))

positive_self_after <- data_self %>% filter(Session == "8") 
positive_self_after<-subset(positive_self_after, select= c("id","mood2_2_happy","mood2_5_cheerful","mood2_6_calm","mood2_8_relaxed","mood2_10_energetic"))

positive_self_after <- data.frame(id=positive_self_after[,1], mean_after =rowMeans(positive_self_after[,2:6]))

self_positive <- inner_join(positive_self_before, positive_self_after, by = "id") 
self_positive <- data.frame(self_positive)
names(self_positive)[7] <- "mean_after"



```



```{r,include=FALSE}

set.seed(1000)
dt_self = sort(sample(nrow(self_positive),nrow(self_positive)*0.7))
train_self <- self_positive[dt_self,]
test_self <- self_positive[-dt_self,]


names(train_self)[2] <- "happy"
names(train_self)[3] <- "cheerful"
names(train_self)[4] <- "calm"
names(train_self)[5] <- "relaxed"
names(train_self)[6] <- "energetic"

names(test_self)[2] <- "happy"
names(test_self)[3] <- "cheerful"
names(test_self)[4] <- "calm"
names(test_self)[5] <- "relaxed"
names(test_self)[6] <- "energetic"

positive_self_reg <-  lm( mean_after ~  happy + cheerful + calm + relaxed + energetic ,data = train_self)
summary(positive_self_reg)


prediction_self <- predict(positive_self_reg,test_self)
test_self["predict"] <- prediction_self
```


firstly, we calculated the MSE to examine the error of the model:

```{r,echo=FALSE,include=TRUE}
MSE_Self = (mean(test_self$mean_after - test_self$predict)^2)
MSE_Self
```
then, we wanted to check the coefficients of the emotions, using R we found the Confidence Intervals for the model parameters ( in confidence level of 0.95 % ):
```{r,echo=FALSE,include=TRUE}
confint(positive_self_reg,level = 0.95)
```
As we can see, all parameters are significant and fall in their confidence intervals.
In conclusion, the model is significant. 

**Provider group regression model : **
we created a multiple regression model according to the positive emotions of the participants in the provider group : 
```{r,echo=FALSE,include=FALSE}
positive_provider_before <- data_provider %>% filter(Session == "1" | Session == "2") %>%distinct(id,.keep_all = TRUE)
positive_provider_before <- subset(positive_provider_before, select= c("id","mood1_2_happy","mood1_5_cheerful","mood1_6_calm","mood1_8_relaxed","mood1_10_energetic"))

positive_provider_after <- data_provider%>% filter(Session == "8")%>% select(c("id","mood1_2_happy","mood1_5_cheerful","mood1_6_calm","mood1_8_relaxed","mood1_10_energetic"))

positive_provider_after <- data.frame(id=positive_provider_after[,1], mean_after =rowMeans(positive_provider_after[,2:6]))


provider_positive <- inner_join(positive_provider_before, positive_provider_after, by = "id") 
provider_positive <- data.frame(provider_positive)
names(provider_positive)[7] <- "mean_after"

```

```{r,include=FALSE}
set.seed(1000)
dt_provider = sort(sample(nrow(provider_positive),nrow(provider_positive)*0.7))
train_provider <- provider_positive[dt_provider,]
test_provider <- provider_positive[-dt_provider,]

names(train_provider)[2] <- "happy"
names(train_provider)[3] <- "cheerful"
names(train_provider)[4] <- "calm"
names(train_provider)[5] <- "relaxed"
names(train_provider)[6] <- "energetic"

names(test_provider)[2] <- "happy"
names(test_provider)[3] <- "cheerful"
names(test_provider)[4] <- "calm"
names(test_provider)[5] <- "relaxed"
names(test_provider)[6] <- "energetic"

positive_provider_reg <-  lm( mean_after ~  happy + cheerful + calm + relaxed + energetic ,data = train_provider)
summary(positive_provider_reg)

prediction_provider <- predict(positive_provider_reg,test_provider)
test_provider["predict"] <- prediction_provider

```


firstly, we calculated the MSE to examine the error of the model:
```{r,echo=FALSE,include=TRUE}
MSE_provider = (mean(test_provider$mean_after - test_provider$predict)^2)
MSE_provider

vif( mod = positive_self_reg )
```

then, we wanted to check the coefficients of the emotions, using R we found the Confidence Intervals for the model parameters (in confidence level of 0.95 %):
```{r,echo=FALSE,include=TRUE}
confint(positive_provider_reg,level = 0.95)
```

```{r,include=FALSE}
data_ques <- read.csv("ControlGroup.csv")
```

```{r,include=FALSE}
only_positive_self <- data.frame(data_ques %>%
                              select("id","happy","cheerful","calm","relaxed","energetic"))


prediction_ques_self <- predict(positive_self_reg,only_positive_self)
only_positive_self["predict_self"] <- prediction_ques_self
```

```{r,include=FALSE}
only_positive_provide <- data.frame(data_ques %>%
                              select("id","happy","cheerful","calm","relaxed","energetic"))

prediction_ques_prov <- predict(positive_provider_reg,only_positive_provide)
only_positive_provide["predict_prov"] <- prediction_ques_prov

```

```{r,include=FALSE}
new_data <- inner_join(only_positive_self, only_positive_provide, by = "id")
mean_prov <- mean(new_data$predict_prov) 
mean_self <- mean(new_data$predict_self)

new_data <- new_data%>%
  select("id","predict_self","predict_prov") %>% pivot_longer(cols=starts_with("predict"))
```

```{r,include=TRUE}
ggplot() + geom_point(data= new_data, aes(x=id, y=value, colour=name),size=2) + theme(axis.title.x=element_blank(),axis.text.x=element_blank(), axis.ticks.x=element_blank()) + labs(y="Predict Value", title="Prediction Findings", subtitle="Results of the Multiple Regresstion Models") + scale_colour_manual(name="Models Prediction:",values = c("blue","plum" ), labels=c("Prediction for the Provider model","Prediction for the Self model")) + geom_hline(yintercept = mean_prov, color='blue') + geom_hline(yintercept = mean_self, color='plum')

```


### Source code

```{r, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
